---
title: "Preliminary research"
author: "Kate Royce"
date: "April 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
cite_options(citation_format = 'pandoc')
P <- rprojroot::find_rstudio_root_file
```

#Introduction

### Time series

A good introduction `r citep('10.1093/ije/dyt092')` has information about common time series tests in epidemiology, as well as sample code for the analyses they suggest.

- Time series: a sequence of data points recorded at regular time intervals. Units are of time, such as days, and underlying population size doesn't matter because it won't change on a short timescale.

- Short timescales are more likely to illuminate causal relationships because they exclude systematic patterns (such as seasons)

### Chaos

[This journal](http://www.cmsim.eu/) is all about chaotic modelling! (Note: this is probably also what edgy fashionistas have as their Twitter bio)

For some reasons my predecessors in Math 53 have written the first [search result](https://math.dartmouth.edu/archive/m53f09/public_html/proj/Jon_writeup.pdf) that comes up when one googles "chaos epidemiology"

Dartmouth strikes again with Lorenz's paper `r citep('10.1175/jas3430.1')` on how to create chaotic models

```{r, include=FALSE}
write.bibtex(file = P("references.bib"))
```

## References

<div id="refs"></div>
